Reply To Examiners

### 2014-06-15 answer_thesis_examiner/chap3.tex
auto

%\replyToComment
%    {
%      Look at Fig 5.13 again, ... can I assume that (b) and (d) are the results of the boxcar filter for homogeneous area?
%      Can these results be compared to the f-MLE results for homogeneous area in Fig 5.12?
%    }
%    {
%      TODO:
%    }

>>>>

\replyToComment
    {
      Look at Fig 5.13 again, ... can I assume that (b) and (d) are the results of the boxcar filter for homogeneous area?
      Can these results be compared to the f-MLE results for homogeneous area in Fig 5.12?
    }
    {
      Yes, Fig 5.13 shows the results of applying the boxcar filter on two homogeneous areas 3dB apart.
      The purpose of Fig 5.13 is to illustrate how AUC (i.e. Area Under the Curve) and MSE can be used to evaluate the performance of speckle filters on heterogeneous area.
      Thus what it shows is not to be taken for comparison with what is shown in Fig. 5.12.
      Fig. 5.15 shows a comparison between the result between boxcar and f-MLE filters over various underlying patterns.
    }

%\begin{mylist}{Something else}
%\item[Whatever]  \LongText 
%\item[Something else] \LongText \LongText
%\end{mylist}
